---
title: "Probability Theory"
---

# Assignment 1

## Assumptions

Assuming the same data as in the Probability tree, the related probabilities and their sum is calculate using the code below.

```{r}
#Constants Definition N<-Not, I<-|. so P(B|A) = P_BIA
P_S<-0.3
P_NS<-1-P_S
P_TIS<-0.2
P_NTIS<-1-P_TIS
P_TINS<-0.6
P_NTINS<-1-P_TINS

#Calculation
P1<-P_S*P_TIS
P2<-P_S*P_NTIS
P3<-P_NS*P_TINS
P4<-P_NS*P_NTINS
Sum_of_P<-P1+P2+P3+P4
```

## Results

P(T ⋂ S ) = 0.06

P(T ⋂ !S ) = 0.24

P(!T ⋂ S ) = 0.42

P(!T ⋂ !S ) = 0.28

Sum of all = 1

# Assignment 2

```{r}
n<-1000

S1<-5*100/1000
S2<-(73+5+33+88)*100/1000
S3<-(423+278+100)*100/1000
```

We can visually note from the Venn diagram:

-   What is the percentage of customers using all three devices?
    -   0.5%
-   What is the percentage of customers using at least two devices?
    -   19.9%
-   What is the percentage of customers using only one device?
    -   80.1%

# Assignment 3

```{r}
P_A<-0.04
P_BIA<-0.97
P_BINA<-0.01

P_B<-(P_BIA*P_A)+(P_BINA*(1-P_A))
P1<-(P_BINA*(1-P_A))/P_B
P2<-(P_BIA*P_A)/P_B

```

These results show that in case the alarm is triggered, there is a possibility of about $19.83$% that the product is flawless and a probability of $80.17$% that the product is faulty.
