---
title: "Statistical Concepts"
---

::: callout-note
You can delete everything in here and start fresh.
:::

-   For each variable, compute the following values. You can use the built-in functions or use the mathematical formulas.
    -   expected value
    -   variance
    -   standard deviation
    
```{r include=FALSE}
library(dplyr)
```

```{r echo=TRUE}

library(dplyr)
#Getting Ages and their Prob

random_vars <- readRDS("C:/Users/Sandipan Mukherjee/Documents/GitHub/cdsba-msandipan/Causal_Data_Science_Data/random_vars.rds")

unique_ages<-unique(random_vars["age"]) %>% as.matrix()
ordered_ages<-unique_ages[order(unique_ages, decreasing = FALSE)]
prob_ages<-prop.table(table(random_vars$age)) %>% unclass()

#Getting Income and their Prob
unique_inc<-unique(random_vars["income"]) %>% as.matrix()
ordered_inc<-unique_inc[order(unique_inc, decreasing = FALSE)]
prob_inc<-prop.table(table(random_vars$income)) %>% unclass()

E_ages<-sum(ordered_ages*prob_ages)
E_inc<-sum(ordered_inc*prob_inc)

#Getting Variance
Var_ages<-var(random_vars$age)
Var_inc<-var(random_vars$income)

Sd_ages<-sd(random_vars$age)
Sd_inc<-sd(random_vars$income)
```

```{r echo=FALSE}
print(paste0("E(Ages): ", E_ages))
print(paste0("E(Income): ", E_inc))
print(paste0("Var(Ages): ", Var_ages))
print(paste0("Var(Income): ", Var_inc))
print(paste0("SD(Ages): ", Sd_ages))
print(paste0("SD(Income): ", Sd_inc))
```

-   Explain, if it makes sense to compare the standard deviations.

It doesn't make sense to compare the standard deviation. Both have different ranges of values in the population therefor comparisons of just the SD gives us no meaningful information.

-   Then, examine the relationship between both variables and compute:

    -   covariance
    -   correlation

```{r echo=TRUE}

library(dplyr)

cov_data<-cov(random_vars$age,random_vars$income)
cor_data<-cor(random_vars$age,random_vars$income)
```

```{r echo=FALSE}
print(paste0("Covariance: ", cov_data))
print(paste0("Correlation: ", cor_data))

```

-   What measure is easier to interpret? Please discuss your interpretation.

Correlation is easier to interpret. Due to the normalization of correlation between -1 to 1 on can precisely determine how strong/weak the relation where has due to the boundless nature of covariance one can only say that the relation between the variables is strong/weak but not its extent.

```{r echo=TRUE}
library(dplyr)
#Set 1
set1<-random_vars$income[random_vars$age<=18]

unique_inc<-unique(set1) %>% as.matrix()
ordered_inc<-unique_inc[order(unique_inc, decreasing = FALSE)]
prob_inc<-prop.table(table(set1)) %>% unclass()

E_set1<-sum(ordered_inc*prob_inc)

#Set 2
set2<-random_vars$income[random_vars$age>=18 & random_vars$age<65]

unique_inc<-unique(set2) %>% as.matrix()
ordered_inc<-unique_inc[order(unique_inc, decreasing = FALSE)]
prob_inc<-prop.table(table(set2)) %>% unclass()

E_set2<-sum(ordered_inc*prob_inc)

#Set3
set3<-random_vars$income[random_vars$age>=65]

unique_inc<-unique(set3) %>% as.matrix()
ordered_inc<-unique_inc[order(unique_inc, decreasing = FALSE)]
prob_inc<-prop.table(table(set3)) %>% unclass()

E_set3<-sum(ordered_inc*prob_inc)
```

```{r echo=FALSE}

print(paste0("E[income|age <= 18]: ", E_set1))
print(paste0("E[income|age ∈ [18,65)]: ", E_set2))
print(paste0("E[income|age >= 65]: ", E_set3))

```
