---
title: "Regression and Statistical Inference"
---

::: callout-note
You can delete everything in here and start fresh.
:::
* Read the data and check the dimensions. How many rows and how many columns does the data have?

181 rows and 82 columns

* Use appropriate commands to get a more detailed look at the data. What data types do you see? How do numbers differ from strings regarding their data type?

str() gives us a quick overview of the different datatypes. typeof() gives us a better view of the type of integer data present. 

```{r}
df <- readRDS("C:/Users/Sandipan Mukherjee/Documents/GitHub/cdsba-msandipan/Causal_Data_Science_Data/car_prices.rds")

str(df)

typeof(df$wheelbase)

```

* Run a linear regression. You want to explain what factors are relevant for the pricing of a car.

Relevant Factors based on p-value:
* carbody
* carwidth 
* enginelocation
* stroke  
* peakrpm
* enginesize 

These factors were chosen based on their p-values indicating that the alternative hypothesis was true instead of the null hypothesis stating that there is a correlation between the variables in question.

```{r}
lm_imp <- lm(price ~ carbody+carwidth+enginelocation+stroke+peakrpm+enginesize, data = df)
summary(lm_imp)
confint(lm_imp, level = 0.95)

```

* Choose one regressor and

  + explain what data type it is and what values it can take on
  + what effect is has on the price and what changing the value would have as a result
  + whether its effect is statistically significant.
  
We can choose to look at the factor "Peak RPM". This factor has integer values ranging from 4200 to 6600. We see that it has a positive effect on the price of the car. As the "Peak RPM" increases the price increases and indicated by the positive coefficient in the linear function. From the p-value 0.000726 we can infer that this factor is highly statistically significant for the inference of the car prices. 


* Add a variable seat_heating to the data and assign a value TRUE for all observations. You can use e.g. df %>% mutate(new_variable = value). Assign it to a new object and run a regression. What coefficient do you get for the new variable seat_heating and how can you explain it?
```{r echo=TRUE}
library(dplyr)
```

```{r}

df<- df %>% mutate(seat_heating = TRUE)
lm_imp <- lm(price ~ carbody+carwidth+enginelocation+stroke+peakrpm+enginesize+seat_heating, data = df)
summary(lm_imp)
```

The coefficients obtained for the new variable "seat_heating" is NA. This can be explained by the fact that since all the values are True thereby this variable is linearly related to other variable leaving us no unique solution to the regression. 