---
title: "Directed Acyclic Graphs"
---

::: callout-note
You can delete everything in here and start fresh.
:::

* Think about example from previous chapter (parking spots) and draw the DAG.

We take the variables as follows
* X is the Parking spots
* Y is the Sales
* Z is the Location

We make the folloing assumption for the dependancies,
* X and Z: Dependant, Location affects the size of the parking spots
* Z and Y: Dependant, Location affects the Sales
* X and Y, conditional on Z: Dependant as the size of the parking lot affects
sales in a fixed location
```{r}

library(dagitty)
library(ggdag)
library(ggplot2)
# Chain
chain <- dagify(
    X ~ Z,
    Y ~ Z,
    Y ~ X,
    coords = list(x = c(Y = 3, Z = 2, X = 1),
                  y = c(Y = 0, Z = 1, X = 0)),
    labels = list(X = "Parking Spots",
                Y = "Sales", 
                Z = "Location")
)

# Plot DAG
ggdag(chain) +
    geom_dag_point(color = "red") +
    geom_dag_text(color = "white") +
    geom_dag_edges(edge_color = "black")+
    geom_dag_label_repel(aes(label = label))
```

* In the data, you find three variables: satisfaction, follow_ups and subscription. Perform the     following steps:

  + regress satisfaction on follow_ups

  + regress satisfaction on follow_ups and account for subscription
  
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
df <- readRDS("C:/Users/Sandipan Mukherjee/Documents/GitHub/cdsba-msandipan/Causal_Data_Science_Data/customer_sat.rds")

# Not Conditioned
lm_1<-lm(satisfaction ~ follow_ups,data=df)
print("Not conditioned coefficients:")
lm_1$coefficients
#Plot
lm_not_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction ))+
  geom_point()+
  stat_smooth(method = "lm", se = F)
lm_not_cond

#Conditioned
lm_2<-lm(satisfaction ~ follow_ups,data=df[df$subscription == "Elite", ])
lm_3<-lm(satisfaction ~ follow_ups,data=df[df$subscription == "Premium", ])
lm_4<-lm(satisfaction ~ follow_ups,data=df[df$subscription == "Premium+", ])
print("Conditioned coefficients accounting for Elite:")
lm_2$coefficients
print("Conditioned coefficients accounting for Premium:")
lm_3$coefficients
print("Conditioned coefficients accounting for Premium+:")
lm_4$coefficients
#Plot
lm_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction,color= subscription ))+ geom_point()+stat_smooth(method = "lm", se = F)
lm_cond


```
  


