---
title: "Randomized Controlled Trials"
---

::: callout-note
You can delete everything in here and start fresh.
:::

-   Check whether the covariates are balanced across the groups. Use a plot to show it.

The covariates are the mobile device users and previous visits of users.

```{r include=FALSE}
library(ggplot2)
library(tidyverse)
```

```{r echo=TRUE}

df <- readRDS("~/GitHub/cdsba-msandipan/Causal_Data_Science_Data/abtest_online.rds")

compare_visits <-  
    ggplot(df, 
           aes(x = chatbot, 
               y = previous_visit, 
               )) +
    stat_summary(geom = "errorbar", 
                 width = .5,
                 fun.data = "mean_se", 
                 fun.args = list(mult=1.96),
                 show.legend = F)
  
df$mobile_device_int<-as.integer(as.logical(df$mobile_device))

compare_devices <-  
    ggplot(df, 
           aes(x = chatbot, 
               y = mobile_device_int, 
               )) +
    stat_summary(geom = "errorbar", 
                 width = .5,
                 fun.data = "mean_se", 
                 fun.args = list(mult=1.96),
                 show.legend = F)
  
compare_visits
compare_devices


```

-   Run a regression to find the effect of chatbot on sales. Both Purchase and Purchase amount show a negative correlation with the usage of chatbots

```{r echo=TRUE}

lm_purchase <- lm(purchase ~ chatbot, data = df)
lm_purchase_amt <- lm(purchase_amount ~ chatbot, data = df)

summary(lm_purchase)
summary(lm_purchase_amt)

```

-   Find subgroup-specific effects by including an interaction. Compute a CATE for one exemplary group. A subgroup could be for example mobile users.

```{r echo=TRUE}

lm_mobile <- lm(purchase_amount ~ chatbot*mobile_device, data = df)
summary(lm_mobile)
```

-   It's not only of interest how much customers buy but also if the buy at all. Then, the dependent variable is binary (either 0 or 1) instead of continuous and the model of choice is the logistic regression. Use the outcome variable purchase and run a logistic regression. The coefficients are not as easily interpretable as before. Look it up and interpret the coefficient for chatbot.

Due to usage of Chatbot being a categorial variable, the coefficient of Chatbot False is 0.49597 and the coefficient for Chatbot True is 0.26786.

```{r echo=TRUE}

lm_purchase <- lm(purchase ~ chatbot, data = df)
summary(lm_purchase)
```
