---
title: "Difference-in-Differences"
---


```{r include=FALSE}
library(ggplot2)
library(tidyverse)
library(dagitty)
library(ggdag)
library(MatchIt)
```

* Manually computing the mean satisfaction for treated and control hospitals before and after the treatment
```{r}
#Check Correlation
df <- readRDS("~/GitHub/cdsba-msandipan/Causal_Data_Science_Data/hospdd.rds")

df_rep<-df
hosp<-unique(df$hospital)
df_rep$hospital<-replace(df$hospital,df$hospital %in% sample(hosp,18),0)
df_rep$hospital<-replace(df_rep$hospital,df_rep$hospital!=0,1)

before_control <- df_rep %>%
  filter(procedure == 0,hospital==0) %>%pull(satis)
before_treatment <- df_rep %>%
  filter(procedure == 0,hospital==1) %>%pull(satis)

after_control <- df_rep %>%
  filter(procedure == 1,hospital==0) %>%pull(satis)
after_treatment <- df_rep %>%
  filter(procedure == 1,hospital==1) %>%pull(satis)

diff_control <- mean(before_control) - mean(after_control)
diff_treatment <- mean(before_treatment) - mean(after_treatment)

diff_diff<-diff_treatment-diff_control
```

* Using a linear regression to compute the estimate. Also, include group and time fixed effects in the regression, i.e. one regressor for each month and one regressor for each hospital:
```{r}
lm_1<-lm(satis~procedure*hospital,data=df_rep)
summary(lm_1)
lm_2<-lm(satis~procedure*(hospital+month),data=df_rep)
summary(lm_2)
lm_3<-lm(satis~procedure*(as.factor(hospital)+as.factor(month)),data=df_rep)
summary(lm_3)

```
Inclusion of the second method would be beneficial as the inclusion of the third method leads to 3 coefficients not defined because of singularities.