---
title: "Instrumental Variables"
---

```{r include=FALSE}
library(ggplot2)
library(tidyverse)
library(dagitty)
library(ggdag)
```

-   Draw a DAG of how you understand the relationships

```{r}
df <- readRDS("~/GitHub/cdsba-msandipan/Causal_Data_Science_Data/rand_enc.rds")
dag_model <- dagify(time_spent~used_ftr,
                    used_ftr~rand_enc,
                    labels = c(
                    "used_ftr" = "used_ftr",
                    "time_spent" = "time_spent",
                    "rand_enc"="rand_enc"
                    ),
                    exposure = "used_ftr",
                    outcome = "time_spent")
ggdag(dag_model, text = FALSE, use_labels = "label")

```

-   Compute the naive, biased estimate.

```{r}
lm_biased<-lm(time_spent~used_ftr,data=df)
summary(lm_biased)
```

-   For the assumptions that can be (partly) tested, check whether they are satisfied by either computing correlations or drawing plots. Argue whether instrumental variable estimation is an adequate procedure.

```{r}
df %>%
   cor() %>% 
   round(2) %>% 
   Matrix::tril()
```

There is a positive correlation between the instrumental variable and the exposure which tells us that a random encouragement trial plays a role in the usage of the test feature.

-   Compute the IV estimate using 2SLS and compare it to the naive estimate. Would you consider the naive estimate biased, and if yes, does it have an upward or downward bias?

```{r}
first_stage<-lm(used_ftr~rand_enc,data=df)
summary(first_stage)

second_stage <- lm(df$time_spent ~ first_stage$fitted.values)
summary(second_stage)
```

Upward Bias since it was leading to increase in relation.
