---
title: "Regression Discontinuity"
---

```{r include=FALSE}
library(ggplot2)
library(tidyverse)
library(dagitty)
library(ggdag)
library(rddensity)
library(dplyr)
```

-   For the first assignment, use the data from the just discussed application (coupon.rds). When conducting a regression discontinuity design, one parameter that is chosen somehow arbitrarily is the bandwidth. Check how sensitive the result is to changing the bandwidth by running the analysis
    -   with half the bandwidth
    -   with double the bandwidth

```{r}
coupon <- readRDS("~/GitHub/cdsba-msandipan/Causal_Data_Science_Data/coupon.rds")
df<-coupon
c0 = 60
bw <- c0 + c(-10, 10)
df_bw_below <- df %>% filter(days_since_last >= bw[1] & days_since_last < c0)
df_bw_above <- df %>% filter(days_since_last >= c0 & days_since_last <= bw[2])
df_bw <- bind_rows(df_bw_above, df_bw_below)
dim(df_bw)

lm_bw <- lm(purchase_after ~ days_since_last_centered + coupon, df_bw)
summary(lm_bw)

bw <- c0 + c(-2, 2)
df_bw_below <- df %>% filter(days_since_last >= bw[1] & days_since_last < c0)
df_bw_above <- df %>% filter(days_since_last >= c0 & days_since_last <= bw[2])
df_bw <- bind_rows(df_bw_above, df_bw_below)
dim(df_bw)

lm_bw <- lm(purchase_after ~ days_since_last_centered + coupon, df_bw)
summary(lm_bw)
```

-   Now consider a different past campaign. For a limited amount of time, for purchases with a total amount of more than 30€ you offered free shipping. The data can be seen in shipping.rds. Have a look at the variable purchase_amount and argue whether it could generally be used as a running variable with a cut-off at 30€.

    -   Use a plot to confirm your argument.

We see that the p-values displayed is 0 which indicates it is a value smaller than 2\^-18 indicating that the null hypothesis that number on either side are different is false. This is also represented in the graph

```{r}
shipping <- readRDS("~/GitHub/cdsba-msandipan/Causal_Data_Science_Data/shipping.rds")
rddd <- rddensity(shipping$purchase_amount, c = 30)
summary(rddd)
rdd_plot <- rdplotdensity(rddd, shipping$purchase_amount, plotN = 100)
```
